Attributions for Poverty in Post-Socialist Countries

### 2014-02-22 article2013.Rmd
5.3. Individual-level tulokset
Jatkan vielä tästä macro-leveleitä

Effect of financial criris        Whether respondents perceives that their household has suffered the financial crisis great or fair amount                             lits

@@

In addition, while calculating R squared or residual standard deviation makes no sense in the case of binomial models, our primary statistical summary of logistic model fit is *deviance*. Deviance can be treated as similar to residual standard deviation for generalized linear models. Basically, deviance is a measure of error, and lower deviance implicates better fit to data. When a random predictor is added to model, we expect deviance to decrease, on average, by 1. When predictor is more informative deviance should decrease more than 1. (Gelman and Hill, 2007). As for getting sensible interpretation of the regression coefficients in logistic regression we can divide the coefficients by 4 to get the probability of certain covariate. The deviance for the empty models both in Tables 3 and 4 indicates that there is "less" to be explained for in the model for individual blame than for social blame. When adding the individual-level predictors to the models, the deviance decreases by 8574 for social blame and 6662 for individual blame.

@@

 In both model *SB individual* and *IB individual* we have four statistically significant predictors. *Perceived low income level* has the highest coefficient of our binary individual level predictors for explaining social blame type of explanation. Coefficient of .36 can be translated so that if respondent perceives belonging to low income group he or she is 8.5 % more likely to blame society for poverty than a non-low income individual. Expected worsening in household income and financial crises experince predict social blame almost in similar manner. *Low education* and *worsened household income* do not contribute in explaining neither of the outcomes.  Being greatly affected by financial crisis makes one 11 % less likely to support for individual blame type of explanation.

>>>>

Effect of financial crisis        Whether respondents perceives that their household has suffered the financial crisis great or fair amount                             lits

@@

In addition, while calculating R squared or residual standard deviation makes no sense in the case of binomial models, our primary statistical summary of logistic model fit is *deviance*. Deviance can be treated as similar to residual standard deviation for generalized linear models. Basically, deviance is a measure of error, and lower deviance implicates better fit to data. When a random predictor is added to model, we expect deviance to decrease, on average, by 1. When predictor is more informative deviance should decrease more than 1 (Gelman and Hill, 2007). As for getting sensible interpretation of the regression coefficients in logistic regression we can divide the coefficients by 4 to get the probability of certain covariate. The deviance for the empty models both in Tables 3 and 4 indicates that there is "less" to be explained for in the model for individual blame than for social blame. When adding the individual-level predictors to the models, the deviance decreases by 8574 for social blame and 6662 for individual blame.

@@

The self-interest hypothesis assumes that those who have financial difficulties or those who have a greater risk to be poor are more inclined to support societal reasons for poverty than those who are not exposed to poverty-related risks. Both Table 3 and Table 4 show four statistically significant individual-level predictors. *Perceived low income level* has the highest coefficient of our binary individual-level predictors for explaining social blame type of explanation. Coefficient of -.36 can be translated so that if respondent perceives belonging to low income group he or she is 8.5 % more likely to blame society for poverty than a non-low income individual. Dependency on public or private transfers, expected worsening in household income in the future and experienced negative effect of financial crisis to household's economy predict the support for social blame explanation almost in similar manner (Table 3). The self-interest hypothesis is also supported in Table 4 which shows that negative experience of financial crisis, transfer dependency, perceived low income level and expected worsening of household income level are statistically associated with individualistic perception of the causes of poverty. For instance, being greatly affected by financial crisis makes one 11 % less likely to support for individual blame type of explanation.

However, there are also individual-level risk factors which are not connected with perceptions of the causes of poverty. First, analyses indicate to some extent equivocal results of the explanatory effect of past experiences: unlike the perceived negative effect of financial crisis, the subjective assessment of negative changes in income is not associated with perceptions. Second, low level of education does not contribute in explaining neither social nor individualistic perception of the causes of poverty.
